Edge sign prediction in general graphs and Correlation Clustering

### 2017-08-25 notations.tex
reorganize CC state of the art

\begin{table*}[thpb]
  \centering
  \caption{List of notations used in this thesis}\label{tab:notations}%
  \vspace{-.5\baselineskip}
  \begin{tabulary}{187mm}{LL}
    \toprule
    Symbol & Meaning \\
    \midrule
    $G$ & An unweighted graph, that can be either directed or undirected \\
    $V$ & The set of all the nodes of a graph, with $|V|=n$. Unless noted otherwise, nodes are indexed from $1$ to $n$ \\
    $E$ & The set of all the edges of a graph, with $|E|=m$ \\
    $u$ & A generic node of $G$. When referring to several nodes, we naturally use $u$, $v$, $w$ and so on. \\
    $(u,v)$ & An undirected edge between nodes $u$ and $v$ \\
    % \euv{} & A directed edge from node $u$ to node $v$ \\
    $\yuv{}$ & The sign of the edge $(u,v)$, which can be either $+1$ or $-1$ \\
    $Y(E)$ & The labeling of $E$, that is the set of all signs of $E$: $Y(E) = \{\yuv : (u,v)\in E\}$ \\
    $\etrain$ & A subset of $E$, given or chosen, of which we observe the signs \\
    $\degr(u)$ & The total degree of node $u$ (that is, the number of edges incident to $u$,
    regardless of their direction) \\
    $\nei(u)$ & The set of all neighbors of $u$, regardless of edge direction. It thus holds
    that $|\nei(u)| = \degr(u)$ \\
    $T$ & An unweighted and undirected tree \\
    $\pathtuv$ & The unique path between $u$ and $v$ in the tree $T$, represented by an ordered list of edges \\
    $|\pathtuv|$ & The length of the path between $u$ and $v$ in the tree $T$, that is its number of edges \\
    \bottomrule
  \end{tabulary}
\end{table*}

>>>>

In this thesis we will sometimes write remarks in a smaller font and with a light blue edging.
\begin{aside}
  Such remarks provide additional information to the topic discussed above, but can be skipped
  without harming the comprehension of the main material.
\end{aside}

\begin{table*}[thpb]
  \centering
  \caption{List of notations used in this thesis}\label{tab:notations}%
  \vspace{-.5\baselineskip}
  \begin{tabulary}{187mm}{LL}
    \toprule
    Symbol & Meaning \\
    \midrule
    \rangek{} & The natural integers from $1$ to $K$, \ie{} $\{1, 2, \ldots, K \}$ \\
    $G$ & An arbitrary graph. It should be clear from the context whether it is weighted or not, and directed or not \\
    $V$ & The set of all the nodes of a graph, with $|V|=n$. Unless noted otherwise, nodes are indexed from $1$ to $n$ \\
    $u$ & A generic node of $G$. When referring to several nodes, we naturally use $u$, $v$, $w$ and so on. \\
    $E$ & The set of all the edges of a graph, with $|E|=m$ \\
    $(u,v)$ & An undirected edge between nodes $u$ and $v$ \\
    \euv{} & A directed edge from node $u$ to node $v$ \\
    $\yuv{}$ & The sign of the edge $(u,v)$, which can be either $+1$ or $-1$ \\
    $Y(E)$ & The labeling of $E$, that is the set of all signs of $E$: $Y(E) = \{\yuv : (u,v)\in E\}$ \\
    $\etrain$ & A subset of $E$, given or chosen, of which we observe the signs \\
    $\degr(u)$ & The total degree of node $u$ (that is, the number of edges incident to $u$,
    regardless of their direction) \\
    $\nei(u)$ & The set of all neighbors of $u$, regardless of edge direction. It thus holds
    that $|\nei(u)| = \degr(u)$ \\
    $T$ & An unweighted and undirected tree \\
    $\pathtuv$ & The unique path between $u$ and $v$ in the tree $T$, represented by an ordered list of edges \\
    $|\pathtuv|$ & The length of the path between $u$ and $v$ in the tree $T$, that is its number of edges \\
    \bottomrule
  \end{tabulary}
\end{table*}

### 2017-08-25 packages.tex
reorganize CC state of the art

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{csquotes}
\usepackage{babel}
\usepackage[heightrounded]{geometry}
\usepackage{setspace}
\usepackage{microtype}
\usepackage[citestyle=alphabetic, bibstyle=ieee-alphabetic, isbn=false, maxnames=1, minnames=1,
sorting=nyvt, backref=true, backend=biber, defernumbers=true,maxbibnames=60]{biblatex}
\AtEveryBibitem{
   \clearfield{arxivId}
   % \clearfield{booktitle}
   % \clearfield{doi}
   \clearfield{eprint}
   \clearfield{eventdate}
   \clearfield{isbn}
   \clearfield{issn}
   % \clearfield{journaltitle}
   \clearfield{month}
   % \clearfield{number}
   % \clearfield{pages}
   \clearfield{series}
   \clearfield{url}
   \clearfield{urldate}
   \clearfield{venue}
   % \clearfield{volume}
   \clearlist{location} % alias to field 'address'
   \clearlist{publisher}
   \clearname{editor}
}
\addbibresource{/home/orphee/data/projects/biblio/library.bib}
\addbibresource{more.bib}
\addbibresource{gtx.bib}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{sidenotes}
\renewcommand{\footnote}[1]{\sidenote{\footnotesize #1}}
\usepackage{enumitem}
\usepackage{tabulary}
\usepackage{bm}
\usepackage{multirow}
\usepackage[marginpar]{todo}
\usepackage[np,autolanguage]{numprint}
\usepackage{listings}
\lstset{frame=none, language=Python, tabsize=4,}
% \usepackage{inconsolata}
\usepackage{nicefrac}
\input{drawing}

@@

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{csquotes}
\usepackage{babel}
\usepackage[heightrounded]{geometry}
\usepackage{setspace}
\usepackage{xspace}
\usepackage{microtype}
\usepackage[citestyle=alphabetic, bibstyle=ieee-alphabetic, isbn=false, maxnames=1, minnames=1,
sorting=nyvt, backref=true, backend=biber, defernumbers=true,maxbibnames=60]{biblatex}
\renewcommand*{\bibfont}{\normalfont\footnotesize}
\AtEveryBibitem{
   % \clearfield{arxivId}
   % \clearfield{booktitle}
   % \clearfield{doi}
   % \clearfield{eprint}
   % \clearfield{eventdate}
   \clearfield{isbn}
   \clearfield{issn}
   % \clearfield{journaltitle}
   \clearfield{month}
   % \clearfield{number}
   % \clearfield{pages}
   \clearfield{series}
   \clearfield{url}
   \clearfield{urldate}
   \clearfield{venue}
   % \clearfield{volume}
   % \clearlist{location} % alias to field 'address'
   \clearlist{publisher}
   \clearname{editor}
}
\addbibresource{/home/orphee/data/projects/biblio/library.bib}
\addbibresource{more.bib}
\addbibresource{gtx.bib}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{import}
\usepackage{mathtools}
\usepackage{sidenotes}
\let\bottomfootnote\footnote
\renewcommand{\footnote}[1]{\sidenote{\footnotesize #1}}
\usepackage[shortlabels]{enumitem}
\usepackage{tabulary}
\usepackage{bm}
\usepackage{multirow}
\usepackage[marginpar]{todo}
\usepackage[np,autolanguage]{numprint}
\usepackage{listings}
\lstset{frame=none, language=Python, tabsize=4,}
% \usepackage{inconsolata}
\usepackage{nicefrac}
\input{drawing}

@@

\usepackage{mdframed}
\newenvironment{aside}%
{\begin{mdframed}[hidealllines=true, leftline=true, innertopmargin=0.5ex, innerbottommargin=0.5ex,
      innermargin=2.3em, leftmargin=2.3em, outermargin=0em, innerleftmargin=0.7em, innerrightmargin=0pt,
      linewidth=1.5pt, skipabove=\baselineskip, skipbelow=\baselineskip,
   linecolor=DodgerBlue!30!White]\small}%
{\end{mdframed}}
\usepackage{stmaryrd}
